---
title: "Power and Sample Size Determination"
author: "Shawn Balcome"
date: "July 22, 2015"
output: slidy_presentation
runtime: shiny
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE}
library("knitr")
library("xtable")
library("pander")
```

## Slides
These slides are hosted at:

https://balcomes.shinyapps.io/power_analysis

The source is available at:



## Review
- Null Hypothesis:  No relationship between, default assumption

- Type 1 Error:  False Positive, falsely reject true $H_0$

- Type 2 Error:  False Negative, fail to reject false $H_0$

----
```{r, results="asis", echo=FALSE}
m <- matrix(c("Type I error", "Correct decision", "Correct decision", "Type II error"),byrow=TRUE,nrow=2)
colnames(m) <- c("$H_0$ is True", "$H_0$ is False")
rownames(m) <- c("Reject $H_0$", "Do not Reject $H_0$")
#kable(as.data.frame(m), format = "markdown")
pandoc.table(as.data.frame(m), format = "rmarkdown")
```

## Cohen
- significance criterion (a)
- the sample size (N)
- population effect size (ES)

## Need to consider
- Significance Level = P(Type I error) = probability of finding an effect that is not there
- Power = 1 - P(Type II error) = probability of finding an effect that is there
Power: Probability that H0 will be rejected when it is false
- Effect Size
- Sample Size

## Effect Size
$d=\frac{M_{group1}-M_{group2}}{SD_{pooled}}$

$SD_{pooled} = \sqrt{\frac{SD^2_{group1}+SD^2_{group2}}{2}}$

## Another
- Confidence Level
- Confidence Interval
- Population
- Sample Size

##R
Programming language useful for Statistics and Plotting

Has a number of packages/libraries catering to many different fields 

Excellent IDE for R
RStudio:  https://www.rstudio.com/

##pwd
```{r, eval=FALSE, echo=TRUE}
install.packages("pwr")
library("pwr")
```

##pwd Table {.smaller}
```{r, results="asis", echo=FALSE}
df <- as.data.frame(matrix(c("pwr.2p.test", "two proportions (equal n)", "pwr.2p2n.test", "two proportions (unequal n)", "pwr.anova.test", "balanced one way ANOVA", "pwr.chisq.test",	"chi-square test", "pwr.f2.test",	"general linear model", "pwr.p.test", "proportion (one sample)", "pwr.r.test",	"correlation", "pwr.t.test",	"t-tests (one sample, 2 sample, paired)", "pwr.t2n.test",	"t-test (two samples with unequal n)"),byrow=TRUE,nrow=9))
names(df) <- c("function",	"power calculations for")
pandoc.table((df), format = "rmarkdown")
```

## Alternative R Packages
- base
- TrialSize:  http://cran.r-project.org/web/packages/TrialSize/index.html

## pwr Demo
```{r, results="asis", echo=TRUE}
library(pwr)
```
For a one-way ANOVA comparing 5 groups, calculate the sample size needed in each group to obtain a power of 0.80, when the effect size is moderate (0.25) and a significance level of 0.05 is employed.
```{r, results="asis", echo=TRUE}
pwr.anova.test(k=5,f=.25,sig.level=.05,power=.8)
```

## pwr Demo Continued
What is the power of a one-tailed t-test, with a significance level of 0.01, 25 people in each group, and an effect size equal to 0.75?
```{r, results="asis", echo=TRUE}
pwr.t.test(n=25,d=0.75,sig.level=.01,alternative="greater")
```

## pwr Demo Continued
Using a two-tailed test proportions, and assuming a significance level of 0.01 and a common sample size of 30 for each proportion, what effect size can be detected with a power of .75? 
```{r, results="asis", echo=TRUE}
pwr.2p.test(n=30,sig.level=0.01,power=0.75)
```

##References {.smaller}
J. Cohen, Statistical Power Analysis for the Behavioral Sciences, 2nd ed. (Erlbaum, Hillsdale, NJ, 1988).

## {.smaller}
```{r, echo = FALSE}
selectInput("pwr_test",
             "Power calculation for:",
             choices = c("two proportions (same sample sizes)" = "pwr.2p.test",
                         "two proportions (different sample sizes)" = "pwr.2p2n.test",
                         "balanced one-way analysis of variance tests" = "pwr.anova.test",
                         "chi-squared tests" = "pwr.chisq.test",
                         "the general linear model" = "pwr.f2.test",
                         "the mean of a normal distribution (known variance)" = "pwr.norm.test",
                         "proportion tests (one sample)" = "pwr.p.test",
                         "correlation test" = "pwr.r.test",
                         "t-tests of means (one sample, two samples and paired samples)" = "pwr.t.test",
                         "two samples (different sizes) t-tests of means" = "pwr.t2n.test"))

################################################################################
# Power calculation for two proportions (same sample sizes) ####################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.2p.test'",
  sidebarPanel(
    radioButtons("missing", "Looking to determine:",
                 choices = c("h", "n", "sig.level", "power"),
                 inline = TRUE),
    radioButtons("alternative", "Alternative Hypothesis:",
                 choices = c("two.sided", "greater", "less"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing != 'h'",
      sliderInput("h",
                  "Effect Size (h)",
                  0,1,0.8)
    ),
    conditionalPanel(
      condition = "input.missing != 'n'",
      sliderInput("n",
                  "Number of observations (n)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing != 'sig.level'",
      sliderInput("sig.level",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing != 'power'",
      sliderInput("power",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing)!=0){
      h <- input$h
      n <- input$n
      sig.level <- input$sig.level
      power <- input$power
      alternative <- input$alternative
      if(input$missing == 'h'){
        h <- NULL
      }
      if(input$missing == 'n'){
        n <- NULL
      }
      if(input$missing == 'sig.level'){
        sig.level <- NULL
      }
      if(input$missing == 'power'){
        power <- NULL
      }
      Result <- as.data.frame(unlist(pwr.2p.test(h,
                                                 n,
                                                 sig.level,
                                                 power,
                                                 alternative)))
      names(Result) <- "Result"
      Result
    }
  )
)

################################################################################
# Power calculation for two proportions (different sample sizes) ###############
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.2p2n.test'",
  sidebarPanel(
    radioButtons("missing_2p2n", "Looking to determine:",
                 choices = c("h", "n1", "n2", "sig.level", "power"),
                 inline = TRUE),
    radioButtons("alternative_2p2n", "Alternative Hypothesis:",
                 choices = c("two.sided", "greater", "less"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_2p2n != 'h'",
      sliderInput("h_2p2n",
                  "Effect Size (h)",
                  0,1,0.8)
    ),
    conditionalPanel(
      condition = "input.missing_2p2n != 'n1'",
      sliderInput("n1_2p2n",
                  "Number of observations (n1)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_2p2n != 'n2'",
      sliderInput("n2_2p2n",
                  "Number of observations (n2)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_2p2n != 'sig.level'",
      sliderInput("sig.level_2p2n",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_2p2n != 'power'",
      sliderInput("power_2p2n",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_2p2n)!=0){
      h_2p2n <- input$h_2p2n
      n1_2p2n <- input$n1_2p2n
      n2_2p2n <- input$n2_2p2n
      sig.level_2p2n <- input$sig.level_2p2n
      power_2p2n <- input$power_2p2n
      alternative_2p2n <- input$alternative_2p2n
      if(input$missing_2p2n == 'h'){
        h_2p2n <- NULL
      }
      if(input$missing_2p2n == 'n1'){
        n1_2p2n <- NULL
      }
      if(input$missing_2p2n == 'n2'){
        n2_2p2n <- NULL
      }
      if(input$missing_2p2n == 'sig.level'){
        sig.level_2p2n <- NULL
      }
      if(input$missing_2p2n == 'power'){
        power_2p2n <- NULL
      }
      Result_2p2n <- as.data.frame(unlist(pwr.2p2n.test(h_2p2n,
                                                        n1_2p2n,
                                                        n2_2p2n,
                                                        sig.level_2p2n,
                                                        power_2p2n,
                                                        alternative_2p2n)))
      names(Result_2p2n) <- "Result"
      Result_2p2n
    }
  )
)

################################################################################
# Balanced one-way analysis of variance tests ##################################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.anova.test'",
  sidebarPanel(
    radioButtons("missing_anova", "Looking to determine:",
                 choices = c("k", "n", "f", "sig.level", "power"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_anova != 'k'",
      sliderInput("k_anova",
                  "Number of groups (k)",
                  1,100,3)
    ),
    conditionalPanel(
      condition = "input.missing_anova != 'n'",
      sliderInput("n_anova",
                  "Number of observations (per group) (n)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_anova != 'f'",
      sliderInput("f_anova",
                  "Effect size (f)",
                  0,1,0.80)
    ),
    conditionalPanel(
      condition = "input.missing_anova != 'sig.level'",
      sliderInput("sig.level_anova",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_anova != 'power'",
      sliderInput("power_anova",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_anova)!=0){
      k_anova <- input$k_anova
      n_anova <- input$n_anova
      f_anova <- input$f_anova
      sig.level_anova <- input$sig.level_anova
      power_anova <- input$power_anova
      if(input$missing_anova == 'k'){
        k_anova <- NULL
      }
      if(input$missing_anova == 'n'){
        n_anova <- NULL
      }
      if(input$missing_anova == 'f'){
        f_anova <- NULL
      }
      if(input$missing_anova == 'sig.level'){
        sig.level_anova <- NULL
      }
      if(input$missing_anova == 'power'){
        power_anova <- NULL
      }
      Result_anova <- as.data.frame(unlist(pwr.anova.test(k_anova,
                                                        n_anova,
                                                        f_anova,
                                                        sig.level_anova,
                                                        power_anova)))
      names(Result_anova) <- "Result"
      Result_anova
    }
  )
)

################################################################################
# chi-squared tests ############################################################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.chisq.test'",
  sidebarPanel(
    radioButtons("missing_chisq", "Looking to determine:",
                 choices = c("w", "N", "df", "sig.level", "power"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_chisq != 'w'",
      sliderInput("w_chisq",
                  "Effect size (w)",
                  0,1,0.80)
    ),
    conditionalPanel(
      condition = "input.missing_chisq != 'N'",
      sliderInput("N_chisq",
                  "Total number of observations (N)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_chisq != 'df'",
      sliderInput("df_chisq",
                  "Degree of freedom (df) (depends on the chosen test)",
                  0,100,6)
    ),
    conditionalPanel(
      condition = "input.missing_chisq != 'sig.level'",
      sliderInput("sig.level_chisq",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_chisq != 'power'",
      sliderInput("power_chisq",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_chisq)!=0){
      w_chisq <- input$w_chisq
      N_chisq <- input$N_chisq
      df_chisq <- input$df_chisq
      sig.level_chisq <- input$sig.level_chisq
      power_chisq <- input$power_chisq
      if(input$missing_chisq == 'w'){
        w_chisq <- NULL
      }
      if(input$missing_chisq == 'N'){
        N_chisq <- NULL
      }
      if(input$missing_chisq == 'df'){
        df_chisq <- NULL
      }
      if(input$missing_chisq == 'sig.level'){
        sig.level_chisq <- NULL
      }
      if(input$missing_chisq == 'power'){
        power_chisq <- NULL
      }
      Result_chisq <- as.data.frame(unlist(pwr.chisq.test(w_chisq,
                                                        N_chisq,
                                                        df_chisq,
                                                        sig.level_chisq,
                                                        power_chisq)))
      names(Result_chisq) <- "Result"
      Result_chisq
    }
  )
)

################################################################################
# The general linear model #####################################################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.f2.test'",
  sidebarPanel(
    radioButtons("missing_f2", "Looking to determine:",
                 choices = c("u", "v", "f2", "sig.level", "power"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_f2 != 'u'",
      sliderInput("u_f2",
                  "Degrees of freedom for numerator (u)",
                  0,100,6)
    ),
    conditionalPanel(
      condition = "input.missing_f2 != 'v'",
      sliderInput("v_f2",
                  "Degrees of freedom for denominator (v)",
                  0,100,6)
    ),
    conditionalPanel(
      condition = "input.missing_f2 != 'f2'",
      sliderInput("f2_f2",
                  "Effect size (f2)",
                  0,1,0.80)
    ),
    conditionalPanel(
      condition = "input.missing_f2 != 'sig.level'",
      sliderInput("sig.level_f2",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_f2 != 'power'",
      sliderInput("power_f2",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_f2)!=0){
      u_f2 <- input$u_f2
      v_f2 <- input$v_f2
      f2_f2 <- input$f2_f2
      sig.level_f2 <- input$sig.level_f2
      power_f2 <- input$power_f2
      if(input$missing_f2 == 'u'){
        u_f2 <- NULL
      }
      if(input$missing_f2 == 'v'){
        v_f2 <- NULL
      }
      if(input$missing_f2 == 'f2'){
        f2_f2 <- NULL
      }
      if(input$missing_f2 == 'sig.level'){
        sig.level_f2 <- NULL
      }
      if(input$missing_f2 == 'power'){
        power_f2 <- NULL
      }
      Result_f2 <- as.data.frame(unlist(pwr.f2.test(u_f2,
                                                    v_f2,
                                                    f2_f2,
                                                    sig.level_f2,
                                                    power_f2)))
      names(Result_f2) <- "Result"
      Result_f2
    }
  )
)

################################################################################
# the mean of a normal distribution (known variance) ###########################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.norm.test'",
  sidebarPanel(
    radioButtons("missing_norm", "Looking to determine:",
                 choices = c("d", "n", "sig.level", "power"),
                 inline = TRUE),
    radioButtons("alternative_norm", "Alternative Hypothesis:",
                 choices = c("two.sided", "greater", "less"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_norm != 'd'",
      sliderInput("d_norm",
                  "Effect Size d=mu-mu0 (d)",
                  0,1,0.8)
    ),
    conditionalPanel(
      condition = "input.missing_norm != 'n'",
      sliderInput("n_norm",
                  "Number of observations (n)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_norm != 'sig.level'",
      sliderInput("sig.level_norm",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_norm != 'power'",
      sliderInput("power_norm",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_norm)!=0){
      d_norm <- input$d_norm
      n_norm <- input$n_norm
      sig.level_norm <- input$sig.level_norm
      power_norm <- input$power_norm
      alternative_norm <- input$alternative_norm
      if(input$missing_norm == 'd'){
        d_norm <- NULL
      }
      if(input$missing_norm == 'n'){
        n_norm <- NULL
      }
      if(input$missing_norm == 'sig.level'){
        sig.level_norm <- NULL
      }
      if(input$missing_norm == 'power'){
        power_norm <- NULL
      }
      Result_norm <- as.data.frame(unlist(pwr.norm.test(d_norm,
                                                        n_norm,
                                                        sig.level_norm,
                                                        power_norm,
                                                        alternative_norm)))
      names(Result_norm) <- "Result"
      Result_norm
    }
  )
)

################################################################################
# Proportion tests (one sample) ################################################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.p.test'",
  sidebarPanel(
    radioButtons("missing_p", "Looking to determine:",
                 choices = c("h", "n", "sig.level", "power"),
                 inline = TRUE),
    radioButtons("alternative_p", "Alternative Hypothesis:",
                 choices = c("two.sided", "greater", "less"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_p != 'h'",
      sliderInput("h_p",
                  "Effect Size (h)",
                  0,1,0.8)
    ),
    conditionalPanel(
      condition = "input.missing_p != 'n'",
      sliderInput("n_p",
                  "Number of observations (n)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_p != 'sig.level'",
      sliderInput("sig.level_p",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_p != 'power'",
      sliderInput("power_p",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_p)!=0){
      h_p <- input$h_p
      n_p <- input$n_p
      sig.level_p <- input$sig.level_p
      power_p <- input$power_p
      alternative_p <- input$alternative_p
      if(input$missing_p == 'h'){
        h_p <- NULL
      }
      if(input$missing_p == 'n'){
        n_p <- NULL
      }
      if(input$missing_p == 'sig.level'){
        sig.level_p <- NULL
      }
      if(input$missing_p == 'power'){
        power_p <- NULL
      }
      Result_p <- as.data.frame(unlist(pwr.p.test(h_p,
                                                        n_p,
                                                        sig.level_p,
                                                        power_p,
                                                        alternative_p)))
      names(Result_p) <- "Result"
      Result_p
    }
  )
)

################################################################################
# Correlation test #############################################################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.r.test'",
  sidebarPanel(
    radioButtons("missing_r", "Looking to determine:",
                 choices = c("n", "r", "sig.level", "power"),
                 inline = TRUE),
    radioButtons("alternative_r", "Alternative Hypothesis:",
                 choices = c("two.sided", "greater", "less"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_r != 'n'",
      sliderInput("n_r",
                  "Number of observations (n)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_r != 'r'",
      sliderInput("r_r",
                  "Linear correlation coefficient (r)",
                  0,1,0.5)
    ),
    conditionalPanel(
      condition = "input.missing_r != 'sig.level'",
      sliderInput("sig.level_r",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_r != 'power'",
      sliderInput("power_r",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_r)!=0){
      n_r <- input$n_r
      r_r <- input$r_r
      sig.level_r <- input$sig.level_r
      power_r <- input$power_r
      alternative_r <- input$alternative_r
      if(input$missing_r == 'n'){
        n_r <- NULL
      }
      if(input$missing_r == 'r'){
        r_r <- NULL
      }
      if(input$missing_r == 'sig.level'){
        sig.level_r <- NULL
      }
      if(input$missing_r == 'power'){
        power_r <- NULL
      }
      Result_r <- as.data.frame(unlist(pwr.r.test(n_r,
                                                        r_r,
                                                        sig.level_r,
                                                        power_r,
                                                        alternative_r)))
      names(Result_r) <- "Result"
      Result_r
    }
  )
)

################################################################################
# t-tests of means (one sample, two samples and paired samples) ################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.t.test'",
  sidebarPanel(
    radioButtons("missing_t", "Looking to determine:",
                 choices = c("n", "d", "sig.level", "power"),
                 inline = TRUE),
    radioButtons("type_t", "Type of t test:",
                 choices = c("two.sample", "one.sample", "paired"),
                 inline = TRUE),
    radioButtons("alternative_t", "Alternative Hypothesis:",
                 choices = c("two.sided", "greater", "less"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_t != 'n'",
      sliderInput("n_t",
                  "Number of observations (per sample) (n)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_t != 'd'",
      sliderInput("d_t",
                  "Effect size (d)",
                  0,1,0.8)
    ),
    conditionalPanel(
      condition = "input.missing_t != 'sig.level'",
      sliderInput("sig.level_t",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_t != 'power'",
      sliderInput("power_t",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_t)!=0){
      n_t <- input$n_t
      d_t <- input$d_t
      sig.level_t <- input$sig.level_t
      power_t <- input$power_t
      type_t <- input$type_t
      alternative_t <- input$alternative_t
      if(input$missing_t == 'n'){
        n_t <- NULL
      }
      if(input$missing_t == 'd'){
        d_t <- NULL
      }
      if(input$missing_t == 'sig.level'){
        sig.level_t <- NULL
      }
      if(input$missing_t == 'power'){
        power_t <- NULL
      }
      Result_t <- as.data.frame(unlist(pwr.t.test(n_t,
                                                        d_t,
                                                        sig.level_t,
                                                        power_t,
                                                        type_t,
                                                        alternative_t)))
      names(Result_t) <- "Result"
      Result_t
    }
  )
)

################################################################################
# Two samples (different sizes) t-tests of means ###############################
################################################################################
conditionalPanel(condition = "input.pwr_test == 'pwr.t2n.test'",
  sidebarPanel(
    radioButtons("missing_t2n", "Looking to determine:",
                 choices = c("n1", "n2", "d", "sig.level", "power"),
                 inline = TRUE),
    radioButtons("alternative_t2n", "Alternative Hypothesis:",
                 choices = c("two.sided", "greater", "less"),
                 inline = TRUE),
    conditionalPanel(
      condition = "input.missing_t2n != 'n1'",
      sliderInput("n1_t2n",
                  "Number of observations in the first sample (n1)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_t2n != 'n2'",
      sliderInput("n2_t2n",
                  "Number of observations in the second sample (n2)",
                  1,10000,100)
    ),
    conditionalPanel(
      condition = "input.missing_t2n != 'd'",
      sliderInput("d_t2n",
                  "Effect size (d)",
                  0,1,0.8)
    ),
    conditionalPanel(
      condition = "input.missing_t2n != 'sig.level'",
      sliderInput("sig.level_t2n",
                  "Significance level (Type I error probability)",
                  0,1,0.05)
    ),
    conditionalPanel(
      condition = "input.missing_t2n != 'power'",
      sliderInput("power_t2n",
                  "Power of test (1 minus Type II error probability)",
                  0,1,0.9)
    )
  ),
        
  renderTable(
    if(length(input$missing_t2n)!=0){
      n1_t2n <- input$n1_t2n
      n2_t2n <- input$n2_t2n
      d_t2n <- input$d_t2n
      sig.level_t2n <- input$sig.level_t2n
      power_t2n <- input$power_t2n
      alternative_t2n <- input$alternative_t2n
      if(input$missing_t2n == 'n1'){
        n1_t2n <- NULL
      }
      if(input$missing_t2n == 'n2'){
        n2_t2n <- NULL
      }
      if(input$missing_t2n == 'd'){
        d_t2n <- NULL
      }
      if(input$missing_t2n == 'sig.level'){
        sig.level_t2n <- NULL
      }
      if(input$missing_t2n == 'power'){
        power_t2n <- NULL
      }
      Result_t2n <- as.data.frame(unlist(pwr.t2n.test(n1_t2n,
                                                      n2_t2n,
                                                      d_t2n,
                                                      sig.level_t2n,
                                                      power_t2n,
                                                      alternative_t2n)))
      names(Result_t2n) <- "Result"
      Result_t2n
    }
  )
)
```


<style>
* { 
	margin: 0; 
	padding: 0; 
}
body { 
	font: 14px/1.4 Georgia, Serif; 
}
#page-wrap {
	margin: 50px;
}
p {
	margin: 20px 0; 
}

	/* 
	Generic Styling, for Desktops/Laptops 
	*/
	table { 
		width:70%; 
    margin-left:15%; 
    margin-right:15%;
		border-collapse: collapse; 
	}
	/* Zebra striping */
	tr:nth-of-type(odd) { 
		background: #eee; 
	}
	th { 
		background: #333; 
		color: white; 
		font-weight: bold; 
	}
	td, th { 
		padding: 6px; 
		border: 1px solid #ccc; 
		text-align: left; 
	}
</style>

